Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-19 paper.tex
Mainly rewriting of sentences
And calls to @amorag and @pacastillo to revise abstract adn introduction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%***TO DO***: rewrite this considering the new contents and results\\

When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory analysis phase using visualisation techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. The
initial methodology was used in a commercial product by Grupo
Trevenque, but the methodology described here improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales from pre-publication data with
remarkable accuracy, thus creating a useful tool for publishers, for whom
% Moreover,
% the proposed method was validated by the company that provided
% the data and incorporated in a business intelligence tool for
% publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation. 
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

%***TO DO***: complete this considering the new contents and results\\
% Instead of just writing this you should say what has changed and
% what should be changed. For instance, the paragraph below probably
% shouldn't - JJ 
Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production and
distribution and storage processes.  When a company is faced with the problem or
releasing a completely new product, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%***TO DO***: rewrite this considering the new contents and results\\
% Has it been done?

When a new book is launched the publisher faces the problem of how
many books should be printed for delivery to bookstores; printing too
many is the main issue, since it implies a loss of investment due to
inventory excess. In this paper, we are tackling the problem of
predicting total sales in order to print the right amount of books and
doing so even before the book has reached the stores.  We have been
working on a data set that includes the complete sales data for books
published in Spain across several years. After an initial exploratory
analysis phase using visualisation techniques, we have applied several
feature selection techniques in order to find out what are the
variables that have more impact on sales, and then used machine
learning to create a model and forecast sales. The initial methodology
was used in a commercial product by Grupo Trevenque, but the
methodology described here improves the running time %with
                                %respect to what?- JJ
and is eventually able to predict sales from pre-publication data with
remarkable accuracy, thus creating a useful tool for publishers, for
whom obtained models can provide a reliable guidance on the decision
process of publishing a book, without human intervention either for
the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

%***TO DO***: complete this considering the new contents and results\\
% Instead of just writing this you should say what has changed and
% what should be changed. For instance, the paragraph below probably
% shouldn't - JJ 
Publishing a book, in the same way as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ
%please someone address this - JJ
